KV Analysis for Non-Expressive performances

### 2020-05-06 material/analysis/stim_n/analysis/ioi_onset.Rmd
move files to analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Non-Expressive performances (ONSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance from teaching-v2.0 (onsets).

@@

>>>>

---
title: 'IOI-Onset Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance (IOI-Onset) from teaching-v2.0.

@@

```{r export, include = FALSE}
fwrite(excluded_cv, "./onset_valid.csv")
```

### 2020-05-06 material/analysis/stim_n/analysis/kv.Rmd
move files to analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Non-Expressive performances (Key Velocity)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
_
Description: This is a rough overview of non-expressive performance from teaching-v2.0 (KV).

@@

>>>>

---
title: 'KV Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
_
Description: This is a rough overview of non-expressive performance (KV) from teaching-v2.0.

@@

```{r export, include = FALSE}
fwrite(excluded_cv, "./kv_valid.csv")
```
